Programs Performance Analysis Toolkit \textit{Adaptor}

### 2013-10-10 keynote/Keynote.tex
Make decent tables instead of screenshots

	\begin{columns}
		\begin{column}{0.5\textwidth}
			\begin{itemize}
				\item \textit{Earth Importance} selected only relevant features
			\end{itemize}
		\end{column}
		\begin{column}{0.5\textwidth}
			\includegraphics[scale=0.375]{feature-ranking}
		\end{column}	
	\end{columns}

@@

	\begin{columns}
		\begin{column}{0.5\textwidth}
			\begin{itemize}
				\item Root Relative Square Error of k Nearest Neighbors --- approx. 5\%
			\end{itemize}
		\end{column}
		\begin{column}{0.5\textwidth}
			\includegraphics[scale=0.5]{evaluation-error}
		\end{column}	
	\end{columns}

@@

\begin{frame}
\frametitle{Resulting model of performance}
	\begin{columns}
		\begin{column}{0.5\textwidth}
			Comparison of models of performance of \textit{ludcmp} program
		\end{column}
		\begin{column}{0.5\textwidth}
			\includegraphics[scale=0.5]{ludcmp-learners-2}
		\end{column}
	\end{columns}
\end{frame}

@@

	\begin{itemize}
		\item Contact information: Michael K. Pankov
		\begin{itemize}
			\item michaelpankov.com
		\end{itemize}
		\item This is an extended and edited version of my diploma defense keynote, given on June 19, 2013
	\end{itemize}
\end{frame}

>>>>

	\begin{center}
	\begin{tabular}{|c|r|r|r|}
	\hline 
	Attribute & Relief F & Mean Square Error & Earth Importance \\ 
	\hline 
	size & 0.268 & 0.573 & 4.9 \\
	cpu\_mhz & 0.000 & 0.006 & 3.3 \\
	width & 0.130 & 0.573 & 0.7 \\
	cpu\_cache & 0.000 & 0.006 & 0.5 \\
	height & 0.130 & 0.573 & 0.0 \\
	\hline 
	\end{tabular} 
	\end{center}

	\begin{itemize}
		\item \textit{Earth Importance} selected only relevant features
	\end{itemize}

@@

	\begin{itemize}
		\item 428 experiments
		\item 1 feature: matrix dimensionality
	\end{itemize}

	\begin{center}
	\begin{tabular}{|c|r|r|r|}
	\hline 
	 & RMSE & RRSE & R2 \\ 
	\hline 
	k Nearest Neighbors & 5.761 & 0.051 & 0.997 \\ 
	Random Forest & 5.961 & 0.052 & 0.997 \\ 
	Linear Regression & 15.869 & 0.139 & 0.981 \\ 
	\hline 
	\end{tabular} 
	\end{center}

	\begin{itemize}
		\item Root Relative Square Error of k Nearest Neighbors --- approx.~5\%
	\end{itemize}

@@

\begin{frame}
\frametitle{Resulting model of performance}

	\begin{itemize}
		\item Comparison of models of performance of \textit{ludcmp} program	
		\item 468 experiments
		\item 2 features: width of matrix, CPU frequency
	\end{itemize}

	\begin{center}
	\begin{tabular}{|c|r|r|r|}
	\hline 
	 & RMSE & RRSE & R2 \\ 
	\hline 
	k Nearest Neigbors & 1.093 & 0.048 & 0.998 \\ 
	Linear Regression & 9.067 & 0.394 & 0.845 \\ 
	\hline
	\end{tabular}
	\end{center}

@@

	\begin{itemize}
		\item Contact information: Michael K. Pankov
		\begin{itemize}
			\item mkpankov@gmail.com
			\item michaelpankov.com
		\end{itemize}
		\item This is an extended and edited version of my diploma defense keynote, given on June 19, 2013
	\end{itemize}
\end{frame}
